---
title: "Alcohol vs Seat choice"
author: "Sabrina Andres"
date: "7 June 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

It appears that those seated in the back have higher variability as opposed to the middle and front. Over 75% of those seated in the back drink more than those seated in the middle or front. Therefore, may reject the null hypothesis.

### get fancy  
```{r}
basicCN <- ggplot(davisdata,aes(x=Seat,y=alcohol))

basicCN + geom_boxplot()
```
```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

It appears that there are more people seated in the back than the front, making seem as though those sitting in the back are drinking more.

The red dots are the outliers. They're the rare few that fall outside the average. 

## Numerical Summarys 

## Inferential Tests

## Conclusions


